---
title: "Iteration and List Columns"
author: Yuqi Wang
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

You can put anything in a list
```{r}
l = list(
vec_numeric = 5:8,
vec_char = c("My", "name", "is", "Jeff"),
vec_logical = c(TRUE, TRUE, TRUE, FALSE),
mat = matrix(1:8, nrow = 2, ncol = 4),
summary = summary(rnorm(100))
)
```

```{r}
l$vec_numeric
l[[1]]
l[["vec_numeric"]]
mean(l[["vec_numeric"]])

```


## `for` loop

create a new list.
```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

```{r}
list_norms
```

Pause and get the old function.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

I can apply the function to each list element.

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```


## Let's try map!

```{r}
map(list_norms, mean_and_sd)
# save the name of the objects in the input list
```

What if we want a different function?

```{r}
output = map(list_norms, IQR)
```


```{r}
output = map_dbl(list_norms, median, .id = "input")
# instead of giving a list, this output several numbers
```


```{r}
output = map_df(list_norms, mean_and_sd, .id = "input")
# put the name of the input list as a separate column
```

## List columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```


```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name == "a")
```

Let's try operations.

```{r}
mean_and_sd(listcol_df$samp[[1]])
```


Can I just map?

```{r}
map(listcol_df$samp, mean_and_sd)
```

So can i add a list column?

```{r}
listcol_df %>% 
  mutate(
    summary = map(samp, mean_and_sd),
    medians = map_dbl(samp, median))
```


## weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

get our list columns

```{r}
weather_nest = weather_df %>% 
  nest(data = date:tmin)
# nest several columns together in a list column
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[1]] # this is the data for central park
```

Suppose I want to regress `tmax` on `tmin` for each station.

This works
```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
```

Let's write a function to do the regression.

```{r}
weather_lm = function(df){
  
  lm(tmax ~ tmin, data = df)
  
}

ouput = vector("list", 3)

for (i in 1:3) {
  output[[i]] = weather_lm(weather_nest$data[[i]])
}


weather_lm(weather_nest$data[[1]])


```

What about a map...

```{r}
weather_nest$data[[1]]

map(weather_nest$data, weather_lm)

```


What about a map in a list column?

```{r}
weather_nest %>% 
  mutate(models = map(data, weather_lm))
```











